The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-04-20 src/static/authors.tex
fixes as per discussion

\author[0000-0001-6637-6922]{James~Tocknell}
\affiliation{School of Mathematical and Physical Sciences, Macquarie University -- Sydney, NSW 2109, Australia.}
\affiliation{Astronomy, Astrophysics and Astrophotonics Research Centre, Macquarie University, Sydney, NSW 2109, Australia}
\affiliation{Australian Astronomical Optics - Macquarie, Macquarie University, Sydney, NSW 2109, Australia}

@@

\author[0000-0003-0353-9741]{Jaime~A.~Alvarado-Montes}
\affiliation{School of Mathematical and Physical Sciences, Macquarie University -- Sydney, NSW 2109, Australia.}
\affiliation{Astronomy, Astrophysics and Astrophotonics Research Centre, Macquarie University, Sydney, NSW 2109, Australia}

@@

\author[0000-0001-5185-9876]{Lee~R.~Spitler}
\affiliation{School of Mathematical and Physical Sciences, Macquarie University -- Sydney, NSW 2109, Australia.}
\affiliation{Astronomy, Astrophysics and Astrophotonics Research Centre, Macquarie University, Sydney, NSW 2109, Australia}
\affiliation{Australian Astronomical Optics - Macquarie, Macquarie University, Sydney, NSW 2109, Australia}

>>>>

\author[0000-0001-6637-6922]{James~Tocknell}
\affiliation{School of Mathematical and Physical Sciences, Macquarie University, Sydney, NSW 2109, Australia.}
\affiliation{Astronomy, Astrophysics and Astrophotonics Research Centre, Macquarie University, Sydney, NSW 2109, Australia}
\affiliation{Australian Astronomical Optics, Macquarie University, Sydney, NSW 2109, Australia}

@@

\author[0000-0003-0353-9741]{Jaime~A.~Alvarado-Montes}
\affiliation{School of Mathematical and Physical Sciences, Macquarie University, Sydney, NSW 2109, Australia.}
\affiliation{Astronomy, Astrophysics and Astrophotonics Research Centre, Macquarie University, Sydney, NSW 2109, Australia}

@@

\author[0000-0001-5185-9876]{Lee~R.~Spitler}
\affiliation{School of Mathematical and Physical Sciences, Macquarie University, Sydney, NSW 2109, Australia.}
\affiliation{Astronomy, Astrophysics and Astrophotonics Research Centre, Macquarie University, Sydney, NSW 2109, Australia}
\affiliation{Australian Astronomical Optics, Macquarie University, Sydney, NSW 2109, Australia}
